---
title: "BNA: Data Collection Tracker"
author: "REACH"
date: "01/04/2022"
output:  
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile), '/bna_field_data_collection_tracker_', format(Sys.Date(), '%Y_%m_%d'),'.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

# read data
df_sample_breakdown <- readr::read_csv(file = "../outputs/sample_breakdown.csv") %>% 
  mutate(providers = str_replace(string = providers, pattern = "apeal", replacement = "ape"),
         providers = str_replace(string = providers, pattern = "include", replacement = "inc"),
         hhid_code = paste0(location, "_", providers))

df_for_colnames <- df_sample_breakdown %>%
  select(location, hhid_code) %>%
  unique()

df_tool_data <- readxl::read_excel(path = "../inputs/BNA_data.xlsx") %>% 
  mutate(uuid = `_uuid`,
         hh_id = str_to_lower(hh_id),
         hhid_code = paste0(location, str_replace(string = str_replace(string = hh_id, 
                                                                       pattern = "_[0-9]{1,2}$|-[0-9]{1,2}$", 
                                                                       replacement = ""), 
                                                  pattern = "^[a-z]{3}_|^[a-z]{3}-", replacement = "_")),
         start_date = as_date(start),
         start = as_datetime(start),
         end = as_datetime(end),
         latitude = as.numeric(`_geopoint_latitude`),
         longitude = as.numeric(`_geopoint_longitude`)) %>% 
  filter(consent == "yes", age >= 18, start_date > as_date("2022-04-06"), 
         !str_detect(string = hh_id, pattern = fixed('test', ignore_case = TRUE))
  )

# days that contain data
df_days_for_data_collection <- df_tool_data %>% select(start_date) %>% unique() %>% arrange(start_date) %>% pull()

df_data_support_cl_log <- df_tool_data %>% 
  select(uuid, location, latitude,	longitude )
# cleaning log handling
df_cl_log <- read_csv(file = "../inputs/combined_checks_bna.csv") %>% 
  mutate(adjust_log = ifelse(is.na(adjust_log), "apply_suggested_change", adjust_log)) %>% 
  mutate(hh_id = str_to_lower(hh_id),
         hhid_code = paste0(location, str_replace(string = str_replace(string = hh_id, 
                                                                       pattern = "_[0-9]{1,2}$|-[0-9]{1,2}$", 
                                                                       replacement = ""), 
                                                  pattern = "^[a-z]{3}_|^[a-z]{3}-", replacement = "_"))) %>% 
  left_join(df_data_support_cl_log, by = "uuid")

# change_response logs that affect stats in the data collection progress
cl_log_change_response <- df_cl_log %>% 
  filter(type == "change_response", 
         !is.na(value),
         reviewed == 1, 
         adjust_log != "delete_log", 
        ) %>% 
  select(uuid, name, value)

# updated tool data
df_updated_tool_data <- df_tool_data

# get uuids from cleaning log
uuids_chg_response <- cl_log_change_response %>% pull(uuid) %>% unique()

for (current_uuid in uuids_chg_response) {
  current_uuid_data <- cl_log_change_response %>% 
    filter(uuid == current_uuid) %>% 
    mutate(value = ifelse(name == "enumerator_id", as.numeric(value), value)) %>% 
    pivot_wider(names_from = "name", values_from = "value", uuid)
  print(current_uuid_data)
  # process current updates
  df_current_updated <- df_updated_tool_data %>% 
    rows_update(y = current_uuid_data, by = "uuid")
  # update the parent dataset with current updates
  df_updated_tool_data <- df_current_updated
}

# enumerator performance data
df_enum_performance <- df_updated_tool_data %>% 
  mutate(int.survey_time_interval = lubridate::time_length(end - start, unit = "min"),
         int.survey_time_interval = ceiling(int.survey_time_interval))

# functions for changing some options in the table
dt_set_options<- function(x){
  DT::datatable(x,
                options = list(
                  autoWidth=F,
                  dom= 't',
                  list(list(width = '20%', targets = list(1,2,3,4,5)))
                )
  )
}

dt_with_modified_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  columnDefs = list(list(className = 'dt-center', targets = list(1,2,3,4,5))),
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

dt_options_fewcols <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}


dt_enum_performance_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                filter = 'top',
                options = list(
                  columnDefs = list(list(className = 'dt-center', targets = list(1,2))),
                  pageLength = 50,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}"),
                  order = list(list(1, 'desc'), list(0, 'asc'), list(3, 'desc'))
                )
  )
}

```

## Summary on the surveys done

>There are **`r nrow(df_updated_tool_data)`** total number of surveys done as of **`r df_days_for_data_collection[length(df_days_for_data_collection)]`**.

### Settlements:  **`r df_updated_tool_data %>% nrow()`** surveys

```{r, echo = FALSE}
# df_refugee_samp_per_settlement <- df_sample_breakdown
# 
# df_cl_surveys_for_deletion <- df_cl_log %>% 
#   filter(type == "remove_survey", reviewed == 1, adjust_log != "delete_log") %>%
#   group_by(location, hhid_code) %>% # could include: hhid_code
#   distinct(uuid) %>%
#   summarise(surveys_for_deletion = n()) %>% 
#   mutate(hhid_code = str_replace(string = hhid_code , pattern = "inc_ucc", replacement = "ucc_inc" ))
# 
# df_updated_tool_data %>% 
#   group_by(location, hhid_code) %>% 
#   summarise(number_of_surveys = n()) %>% 
#   arrange(location) %>% 
#   right_join(df_refugee_samp_per_settlement, by = "hhid_code") %>% 
#   left_join(df_cl_surveys_for_deletion, by = "hhid_code") %>% 
#   mutate(number_of_surveys = ifelse(is.na(number_of_surveys), 0, number_of_surveys),
#          surveys_for_deletion = ifelse(is.na(surveys_for_deletion), 0, surveys_for_deletion),
#          int.surveys_and_deletion = number_of_surveys - surveys_for_deletion,
#          remaining_surveys = sample_size - int.surveys_and_deletion ) %>%
#   # select(-location) %>% 
#   # rename(location = location.x) %>%
#   # mutate(location = location.y) %>%
#   # select(-c(int.surveys_and_deletion, location.y)) %>%
#   dt_with_modified_options()

```

### Daily enumerator performance

The average survey time for all the data is: **`r round(mean(df_enum_performance$int.survey_time_interval), 0)`** Minutes

```{r, echo = FALSE}

df_enum_performance %>% 
  group_by(location, start_date, enumerator_id) %>% 
  summarise(number_of_interviews_done = n(), `average_survey_time(minutes)` = round(mean(int.survey_time_interval, na.rm = TRUE), 0)) %>% 
  dt_enum_performance_options()
```

## Looking into the cleaning log

### Number of issues by issue_id

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(issue_id) %>% 
  summarise(number_of_issues_by_issue_id = n()) %>%
  dt_options_fewcols()
```
### Number of issues by enumerator

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(enumerator_id) %>% 
  summarise(number_of_issues_by_enumerator_id = n()) %>%
  dt_options_fewcols()
```

### Number of issues by enumerator and issue_id

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(enumerator_id, issue_id) %>% 
  summarise(number_of_issues_by_enumerator_and_issue_id = n()) %>%
  dt_options_fewcols()
```

### Enumerators with surveys for deletion

```{r, echo = FALSE}
df_cl_log %>% 
  filter(type == "remove_survey", reviewed == 1, adjust_log != "delete_log") %>% 
  group_by(enumerator_id) %>% 
  summarise(number_of_surveys_for_deletion_by_enumerator = n()) %>%
  dt_options_fewcols()
```